### 2021-02-18 architecture.tex
Improve Architecture

The precedence recommender is a system that takes
a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
and produces a precedence over the symbols $\Sigma$ as the output.

The architecture is designed so that the recommender can be trained
on the results of solver executions with random precedences.
The recommender is parameterized by weight tensors
whose values can be trained by gradient descent.
\todo{Ensure we have defined ``gradient descent''.}
The goal of the training is to find parameter values
such that the recommender produces precedences
that are likely to yield a successful proof in few iterations of the saturation loop.

>>>>

The precedence recommender is a system that takes
a \gls{cnf} problem $P = (\Sigma, \mathit{Cl})$ as the input,
and produces a precedence $\pi^*$ over the symbols $\Sigma$ as the output.

The architecture is designed so that the recommender can be trained
on the results executions of an \gls{atp} on various problems with random precedences.
The recommender is parameterized by weight tensors
whose values can be trained by gradient descent.
\todo{Ensure we have defined ``gradient descent''.}
The goal of the training is to find parameter values
such that the recommender produces precedences
that are likely to yield a successful proof in few iterations of the saturation loop.
\todo{FB: Too vague?}
